---
title: "PSY 8960 Week 8 Project"
author: Richard N. Landers
output: 
  html_document:
    df_print: paged
---

# Reproducible Image and Online Resources
An image of this project as of *March 20, 2023* can be accessed by [clicking this link](https://mybinder.org/v2/gh/rnlanders/psy8960-sp2023/HEAD).

An interactive web app is available by [clicking this link instead](https://tntlab.shinyapps.io/shiny_week8/).

# Script Settings and Resources
```{r section2, message=F}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

# Data Import and Cleaning
I reverse coded Q5, coded gender as factor and a date flag for use in the shiny app, and calculated means for display in both the shiny app and in this notebook.
```{r section3}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(
    # timeStart = ymd_hms(timeStart),
    q5_rev = 6 - q5,
    gender = factor(gender, levels=c("M","F"), labels=c("Male","Female")),
    q1q6_mean = rowMeans(across(c(q1:q4,q5_rev,q6))),
    q8q10_mean = rowMeans(across(q8:q10)),
    after_aug2017_flag = timeEnd > "2017-08-01 00:00:00",
  )
```

# Visualization
Used select to subset q vars from data; displayed plot based on two means calculated in data cleaning step
```{r section4, echo=F, message=F}
select(week8_tbl, q1:q4, q5_rev, q6)
ggplot(week8_tbl,
       aes(x = q1q6_mean, y = q8q10_mean)) +
       geom_point() +
       geom_smooth(method="lm", color="purple")
```

# Analysis
I calculated the correlation between the two means and observed a correlation of `r cor.test(week8_tbl$q1q6_mean, week8_tbl$q8q10_mean)$estimate`. We failed to reject the null. Terrible news.
```{r section5}
cor.test(week8_tbl$q1q6_mean, week8_tbl$q8q10_mean)
```

# Data Export
We needed to create a skinny data file, i.e., a file containing only the necessary data to create the app. RDS allows us to do this in the native R data format which prevents any loss of information as we might see on export/import with CSV/TSV.
```{r section6}
week8_tbl %>%
  select(q1q6_mean, q8q10_mean, 
         gender, after_aug2017_flag) %>%
  saveRDS("../shiny/shiny_week8/shiny_input.RDS")
```